\documentclass[11pt,]{article}
\usepackage[sc, osf]{mathpazo}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}




\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

% Now begins the stuff that I added.
% ----------------------------------

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\large\bf}
\subsectionfont{\rmfamily\mdseries\normalsize\scshape}


% Make lists without bullets
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
  }
}{
  \end{list}
}


% Make parskips rather than indent with lists.
\usepackage{parskip}
\usepackage{titlesec}
\titlespacing\section{0pt}{12pt plus 4pt minus 2pt}{4pt plus 2pt minus 2pt}
\titlespacing\subsection{0pt}{12pt plus 4pt minus 2pt}{4pt plus 2pt minus 2pt}

% Use fontawesome. Note: you'll need TeXLive 2015. Update.
\usepackage{fontawesome}

% Fancyhdr, as I tend to do with these personal documents.
\usepackage{fancyhdr,lastpage}
\pagestyle{fancy}
\renewcommand{\headrulewidth}{0.0pt}
\renewcommand{\footrulewidth}{0.0pt}
\lhead{}
\chead{}
\rhead{}
\lfoot{
\cfoot{\scriptsize  Daniel Katz - CV }}
\rfoot{\scriptsize \thepage/{\hypersetup{linkcolor=black}\pageref{LastPage}}}

% Always load hyperref last.
\usepackage{hyperref}
\PassOptionsToPackage{usenames,dvipsnames}{color} % color is loaded by hyperref

\hypersetup{unicode=true,
            pdftitle={Daniel Katz:  CV (Curriculum Vitae)},
            pdfauthor={Daniel Katz},
            colorlinks=true,
            linkcolor=blue,
            citecolor=Blue,
            urlcolor=blue,
            breaklinks=true, bookmarks=true}
\urlstyle{same}  % don't use monospace font for urls

% Make AP style (kinda) dates for the updated/today field

\usepackage{datetime}
\newdateformat{apstylekinda}{%
  \shortmonthname[\THEMONTH]. \THEDAY, \THEYEAR}

\begin{document}


\centerline{\huge \bf Daniel Katz}

\vspace{2 mm}

\hrule

\vspace{2 mm}

\moveleft.5\hoffset\centerline{Graduate Student}

\moveleft.5\hoffset\centerline{ \faEnvelopeO \hspace{1 mm} \href{mailto:}{\tt \href{mailto:dkatz@ucsb.edu}{\nolinkurl{dkatz@ucsb.edu}}} \hspace{1 mm}  \faPhone \hspace{1 mm}  310-800-8354  \hspace{1 mm}  \faGithub \hspace{1 mm} \href{http://github.com/danielbkatz}{\tt danielbkatz} \hspace{1 mm}     \faGlobe \hspace{1 mm} \href{http://dbkatz.com}{\tt dbkatz.com}    | \emph{Updated:} \apstylekinda\today}

\vspace{2 mm}

\hrule

\vspace{5mm}
\# EDUCATION

\hypertarget{university-of-california-santa-barbara}{%
\subsection{University of California, Santa
Barbara}\label{university-of-california-santa-barbara}}

\textbf{PhD} (2021): Education - Quantitative Research Methods and
Philosophy of Measurement\\
\hspace*{0.333em}\hspace*{0.333em}Thesis: Fairness and Uncertainty in
Academic Testing\\
\hspace*{0.333em}\hspace*{0.333em}Advisor: Andrew Maul

\textbf{M.A.} (2017) Education - Quantitative Research Methods\\
\hspace*{0.333em}\hspace*{0.333em} Thesis: Validating a Multidimensional
Measure of Reading Strategy Use

\textbf{BA} (2011), Political Science, Minor in History

\textbackslash{} \textbackslash{} \# RESEARCH INTERESTS

~~ The Rasch Model\\
\hspace*{0.333em}\hspace*{0.333em} Fairness and Ethincs\\
\hspace*{0.333em}\hspace*{0.333em} Measurement Invariance\\
\hspace*{0.333em}\hspace*{0.333em} Explanatory Item Response Models\\
\hspace*{0.333em}\hspace*{0.333em} Philosophy of Measurement, Language,
and Probability\\
\hspace*{0.333em}\hspace*{0.333em} Causal Inference

\hypertarget{relevant-experience}{%
\section{RELEVANT EXPERIENCE}\label{relevant-experience}}

\textbf{University of Florida, Virtual Learning Lab -- IES Funded Grant}
(2019-Present)\\
\hspace*{0.333em}\hspace*{0.333em} Supervisor: Anne Corinne Manley ~~
Role: Graduate Student Extern -- IRT/Simulation focus

\textbf{UCSB Center for Innovative Teaching, Research, and Learning
(CITRAL)} (2018-Present)\\
\hspace*{0.333em}\hspace*{0.333em} Supervisor: Linda Adler-Kassner\\
\hspace*{0.333em}\hspace*{0.333em} Role: Graduate Student Researcher in
Assessment and Evaluation

\textbf{New York City Department of Education: Assessment, Design, and
Evaluation} (Summer 2018)\\
\hspace*{0.333em}\hspace*{0.333em} Supervisor: Ronli Diakow\\
\hspace*{0.333em}\hspace*{0.333em} Role: Graduate Student Psychometrics
Intern -- Applying IRT and Explanatory IRT Models

\textbf{California Dropout Research Project (CDRP); Get Focused Stay
Focused Evaluation} (2016-2019)\\
\hspace*{0.333em}\hspace*{0.333em} PI: Russell Rumberger\\
\hspace*{0.333em}\hspace*{0.333em} Role: Graduate Student Researcher

\textbf{UCSB General Education Assessment Project, Office of
Institutional Research} (2016-2018)\\
\hspace*{0.333em}\hspace*{0.333em} PI: Linda Adler-Kassner, Co-Interim
Dean of UCSB Undergraduate Education\\
\hspace*{0.333em}\hspace*{0.333em} Role: Graduate Student Researcher

\hypertarget{published-work}{%
\section{PUBLISHED WORK}\label{published-work}}

Arya, Diana, Clairmont, A. \textbf{Katz, D} \& Maul, A. (2020) Measuring
Reading Strategy Use, \emph{Educational ~~ Assessment}, 25:1, 5-30, DOI:
10.1080/10627197.2019.1702464

Maul, A. and \textbf{Katz, D}. (2018). Internal Validity. In B. Frey
(Editor), The SAGE Encyclopedia of ~~Educational Research, Measurement,
and Evaluation. Thousand Oaks, CA: SAGE.

\textbf{Katz, D.} (2017, May). An Update: The Narrowing California High
School Graduation Gap between ~~Black, Latino, and White Students. (CDRP
Statistical Brief No.~24). Retrieved from
~~\url{http://cdrpsb.org/pubs_statbriefs.htm}

\textbf{Katz, D.} (2017, March). The Narrowing California High School
Graduation Gap between Black, ~~Latino, and White Students. (CDRP
Statistical Brief No.~23). Retrieved from
~~\url{http://cdrpsb.org/pubs_statbriefs.htm}. The Narrowing California
High School Graduation Gap ~~between Black, Latino, and White Students

\hypertarget{conference-presentations}{%
\section{CONFERENCE PRESENTATIONS}\label{conference-presentations}}

\textbf{Katz, D.} and Diakow, R. (2019, April). Using Explanatory Item
Response Theory Models to Re-Examine ~~Fairness in Psychometrics. Paper
to be presented at the National Council on Measurement ~~in Education
(NCME) April 4-8, 2019. Toronto.

\textbf{Katz, D.}, Nylund-Gibson, K., Furlong, M. (2019, April). Is One
Item Enough? Examining ~~Affect-Laden Survey Items Using Mixture
Modelling with Distal Outcomes. Paper presented ~~at American
Educational Research Association Annual Meeting, April 5-9, 2019.
Toronto.\\
\textbf{Best Graduate Student Paper in the AERA Survey Special Interest
Group Sig}

\textbf{Katz, D.}, Clairmont, A., Arya, D., \& Maul, A., (2018, April).
Measuring Reading Strategy Use in a ~~Multilingual Context. Paper
presented at American Educational Research Association Annual ~~Meeting,
April 13-17, 2018. New York.

\textbf{Katz, D.}, Clairmont, A., Arya, D. \& Maul, A. (2018, April).
Measuring Reading Strategy Use in a ~~Multidimensional, Multilingual
Context. Paper presented at the International Objective ~~Measurement
Workshop (IOMW), April 10-12, 2018. New York.

\hypertarget{select-in-progress-work}{%
\section{SELECT IN PROGRESS WORK}\label{select-in-progress-work}}

Clairmont, A. \& Katz D. (in preperation) Using Rasch Measurement Theory
for Program Evaluation: A ~~ Methods Note. To be submitted to
\emph{American Journal of Evaluation}

Katz, D., Maul A., Clairmont, A (2021) Tools from philosophy of language
for increasing transparency ~~ in psychological measurement"

Reconsidering fairness in educational assessment: using tools from
ethics, causal inference, and ~~ psychometrics

Measuring subjective well-being and other constructs in positive
psychology using mixture modelling ~~ approaches (with an emphasis on
educational settings)

\hypertarget{teaching-experience}{%
\section{TEACHING EXPERIENCE}\label{teaching-experience}}

\textbf{Instructor}\\
\hspace*{0.333em}\hspace*{0.333em} One Day Workshop: UCSB Methods U - An
Introduction to R: Data Cleaning, Wrangling, and Visualizing ~~
Implementing Explanatory IRT via the R package, TAM

\textbf{Teaching Assistant} ~~ Education 214C, Linear Models for Data
Analysis (and categorical data analysis), Spring 2018 ~~ Education 214B,
Inferential Statistics, Winter 2018 ~~ Education 214A, Introductory
Statistics, Fall 2017

\hypertarget{organization-committee-memberships}{%
\section{ORGANIZATION \& COMMITTEE
MEMBERSHIPS}\label{organization-committee-memberships}}

~~ Graduate Student Representative -- NCME Committee on informing
assessment policy and practice ~~ American Educational Research
Association ~~ National Council on Measurement in Education ~~ Society
for the Improvement of Psychological Sciences

\hypertarget{statistical-software}{%
\section{STATISTICAL SOFTWARE}\label{statistical-software}}

~~ R ~~~~ Commonly used stats packages: TAM, mirt, lme4, Lavaan, plm
~~~~ Other packages: tidyverse, Rmarkdown, xaringan ~~ Mplus ~~ Stata
(Basic Knowledge)\\
\hspace*{0.333em}\hspace*{0.333em} Tableau (Basic Knowledge)\\
\hspace*{0.333em}\hspace*{0.333em} Git and Gitub (Basic Knowledge)\\
\hspace*{0.333em}\hspace*{0.333em} Stan/rstan (Beginner)\\
\hspace*{0.333em}\hspace*{0.333em} Dedoose (Beginner)

\end{document}

